---
title: "Data Dictionary"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=F, message=F)

library( knitr )


```



## Index of Variable Groups ("parts")

*These groups are based upon the [2016 IRS 990 Forms and Schedules](https://github.com/Nonprofit-Open-Data-Collective/irs-efile-master-concordance-file/tree/master/990_forms).

### FORM 990-PC (FULL)

* Part I    - Summary  
* Part II   - Signature Block  
* Part III  - Statement of Program Service Accomplishments  
* Part IV   - Checklist of Required Schedules  
* Part V    - Statements Regarding Other IRS Filings and Tax Compliance  
* Part VI   - Governance, Management, and Disclosure  
    * Section A. Governing Body and Management  
    * Section B. Policies  
    * Section C. Disclosure  
* Part VII  - Compensation of Officers, Directors, Trustees, Key Employees, Highest Compensated Employees, and Independent Contractors  
    * Section A. Officers, Directors, Trustees, Key Employees, and Highest Compensated Employees  
    * Section B. Independent Contractors  
* Part VIII - Statement of Revenue  
* Part IX   - Statement of Functional Expenses  
* Part X    - Balance Sheet  
* Part XI   - Reconciliation of Net Assets  
* Part XII  - Financial Statements and Reporting  
 
  
### SCHEDULE A - PUBLIC CHARITY STATUS AND PUBLIC SUPPORT (PC AND EZ FILERS)

*Complete if the organization is a section 501(c)(3) organization or a section 4947(a)(1) nonexempt charitable trust.*

* Part I    - Reason for Public Charity Status
* Part II   - Support Schedule for Organizations Described in Sections 170(b)(1)(A)(iv) and 170(b)(1)(A)(vi)
** Section A. Public Support
** Section B. Total Support
** Section C. Computation of Public Support Percentage
* Part III  - Support Schedule for Organizations Described in Section 509(a)(2)
    * Section A. Public Support
    * Section B. Total Support
    * Section C. Computation of Public Support Percentage
    * Section D. Computation of Investment Income Percentage
* Part IV   - Supporting Organizations
    * Section A. All Supporting Organizations
    * Section B. Type I Supporting Organizations
    * Section C. Type II Supporting Organizations
    * Section D. All Type III Supporting Organizations
    * Section E. Type III Functionally Integrated Supporting Organizations
* Part V    - Type III Non-Functionally Integrated 509(a)(3) Supporting Organizations            
    * Section A - Adjusted Net Income
    * Section B - Minimum Asset Amount
    * Section C - Distributable Amount
    * Section D - Distributions
    * Section E - Distribution Allocations
* Part VI   - Supplemental Information (UNSTRUCTURED - CAN WE CODE THIS?)           



### SCHEDULE B - SCHEDULE OF CONTRIBUTORS (PC, EZ, AND PF FILERS)

* Header    - Type of Organization
* Part I    - Contributors
* Part II   - Noncash Property
* Part III  - Exclusively religious, charitable, contributions above $1,000



### SCHEDULE C - POLITICAL CAMPAIGN AND LOBBYING ACTIVITIES (PC AND EZ FILERS)

* Part I-A  - Complete if the organization is exempt under section 501(c) or is a section 527 organization.
* Part I-B  - Complete if the organization is exempt under section 501(c)(3)
* Part I-C  - Complete if the organization is exempt under section 501(c), except section 501(c)(3)
* Part II-A - Complete if the organization is exempt under section 501(c)(3) and filed Form 5768 (election under section 501(h))
* Part II-B - Complete if the organization is exempt under section 501(c)(3) and has NOT filed Form 5768 (election under section 501(h))
* Part IIIA - Complete if the organization is exempt under section 501(c)(4), section 501(c)(5), or section 501(c)(6)
* Part IIIB - Complete if the organization is exempt under section 501(c)(4), section 501(c)(5), or section 501(c)(6) and if either (a)     
    * BOTH Part III-A, lines 1 and 2, are answered “No,” OR (b) Part III-A, line 3, is answered “Yes.”
* Part IV   - Supplemental Information



### SCHEDULE D - SUPPLEMENTAL FINANCIAL STATEMENTS (PC FILERS ONLY)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 6, 7, 8, 9, 10, 11a, 11b, 11c, 11d, 11e, 11f, 12a, or 12b.*

* Part I    - Organizations Maintaining Donor Advised Funds or Other Similar Funds or Accounts
* Part II   - Conservation Easements
* Part III  - Organizations Maintaining Collections of Art, Historical Treasures, or Other Similar Assets
* Part IV   - Escrow and Custodial Arrangements
* Part V    - Endowment Funds
* Part VI   - Land, Buildings, and Equipment
* Part VII  - Investments—Other Securities
* Part VIII - Investments—Program Related
* Part IX   - Other Assets
* Part X    - Other Liabilities
* Part XI   - Reconciliation of Revenue per Audited Financial Statements With Revenue per Return
* Part XII  - Reconciliation of Expenses per Audited Financial Statements With Expenses per Return
* Part XIII - Supplemental Information (UNSTRUCTURED)



### SCHEDULE E - SCHOOLS (PC AND EZ FILERS)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 13, or Form 990-EZ, Part VI, line 48.*

* Part I    - General Info
* Part II   - Supplemental Information



### SCHEDULE F - STATEMENT OF ACTIVITIES OUTSIDE THE UNITED STATES (PC FILERS ONLY)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 14b, 15, or 16.*

* Part I    - General Information on Activities Outside the United States
* Part II   - Grants and Other Assistance to Organizations or Entities Outside the United States
* Part III  - Grants and Other Assistance to Individuals Outside the United States
* Part IV   - Foreign Forms
* Part V    - Supplemental Information (UNSTRUCTURED)



### SCHEDULE G - SUPPLEMENTAL INFORMATION REGARDING FUNDRAISING OR GAMING ACTIVITIES (PC AND EZ FILERS)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 17, 18, or 19, or if the organization entered more than $15,000 on Form 990-EZ, line 6a.*

* Part I    - Fundraising Activities
* Part II   - Fundraising Events
* Part III  - Gaming
* Part IV   - Supplemental Information (UNSTRUCTURED)



### SCHEDULE H - HOSPITALS (PC FILERS ONLY)

*Complete if the organization answered “Yes” on Form 990, Part IV, question 20.*

* Part I    - Financial Assistance and Certain Other Community Benefits at Cost
* Part II   - Community Building Activities
* Part III  - Bad Debt, Medicare, & Collection Practices
    * Section A. Bad Debt Expense
    * Section B. Medicare
    * Section C. Collection Practices
* Part IV   - Management Companies and Joint Ventures
* Part V    - Facility Information
    * Section A. Hospital Facilities
    * Section B. Facility Policies and Practices
        * Community Health Needs Assessment
        * Financial Assistance Policy (FAP)
        * Billing and Collections
        * Policy Relating to Emergency Medical Care
        * Charges to Individuals Eligible for Assistance Under the FAP (FAP-Eligible Individuals)
    * Section C. Supplemental Information for Part V, Section B
    * Section D. Other Health Care Facilities That Are Not Licensed, Registered, or Similarly Recognized as a Hospital Facility
* Part VI   - Supplemental Information





### SCHEDULE I - GRANTS AND OTHER ASSISTANCE TO ORGANIZATIONS, GOVERNMENTS, AND INDIVIDUALS IN THE UNITED STATES (PC FILERS ONLY)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 21 or 22.*


* Part I    - General Information on Grants and Assistance
* Part II   - Grants and Other Assistance to Domestic Organizations and Domestic Governments
* Part III  - Grants and Other Assistance to Domestic Individuals.
* Part IV   - Supplemental Information


#### SCHEDULE I1 - Continuation Sheet for Schedule I (Form 990)

* Part I    - Continuation of Grants and Other Assistance to Governments and Organizations in the United States
* Part II   - Continuation of Grants and Other Assistance to Individuals in the United States


### SCHEDULE J - COMPENSATION INFORMATION (PC FILERS ONLY)

Complete if the organization answered “Yes” on Form 990, Part IV, line 23

* Part I    - Questions Regarding Compensation
* Part II   - Officers, Directors, Trustees, Key Employees, and Highest Compensated Employees
* Part III  - Supplemental Information


#### SCHEDULE J1 - CONTINUATION SHEET FOR SCHEDULE J

* Part I    - Continuation of Officers, Directors, Trustees, Key Employees, and Highest Compensated Employees

#### SCHEDULE J2 - CONTINUATION SHEET FOR FORM 990

*Attach to Form 990 to list additional information for Form 990, Part VII, Section A, line 1a.*

* Part I    - Continuation of Officers, Directors, Trustees, Key Employees, and Highest Compensated Employees



### SCHEDULE K - SUPPLEMENTAL INFORMATION ON TAX-EXEMPT BONDS (PC FILERS ONLY)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 24a. Provide descriptions, explanations, and any additional information in Part VI.*

* Part I    - Bond Issues
* Part II   - Proceeds
* Part III  - Private Business Use
* Part IV   - Arbitrage
* Part V    - Procedures To Undertake Corrective Action
* Part VI   - Supplemental Information



### SCHEDULE L - TRANSACTIONS WITH INTERESTED PERSONS (PC AND EZ FILERS)

*Complete if the organization answered “Yes” on Form 990, Part IV, line 25a, 25b, 26, 27, 28a, 28b, or 28c, or Form 990-EZ, Part V, line 38a or 40b.*

* Part I    - Excess Benefit Transactions
* Part II   - Loans to and/or From Interested Persons
* Part III  - Grants or Assistance Benefiting Interested Persons
* Part IV   - Business Transactions Involving Interested Persons
* Part V    - Supplemental Information




### SCHEDULE M - NONCASH CONTRIBUTIONS (PC FILERS ONLY)

*Complete if the organizations answered “Yes” on Form 990, Part IV, lines 29 or 30.*

* Part I    - Types of Property
* Part II   - Supplemental Information




### SCHEDULE N - LIQUIDATION, TERMINATION, DISSOLUTION, OR SIGNIFICANT DISPOSITION OF ASSETS (PC AND EZ FILERS)

*Complete if the organization answered "Yes" on Form 990, Part IV, lines 31 or 32; or Form 990-EZ, line 36.*

* Part I    - Liquidation, Termination, or Dissolution
* Part II   - Sale, Exchange, Disposition, or Other Transfer of More Than 25% of the Organization’s Assets
* Part III  - Supplemental Information




### SCHEDULE O - SUPPLEMENTAL INFORMATION TO FORM 990 OR 990-EZ



### SCHEDULE R - RELATED ORGANIZATIONS AND UNRELATED PARTNERSHIPS (PC FILERS ONLY)

*Complete if the organization answered "Yes" on Form 990, Part IV, line 33, 34, 35b, 36, or 37.*

* Part I    - Identification of Disregarded Entities
* Part II   - Identification of Related Tax-Exempt Organizations
* Part III  - Identification of Related Organizations Taxable as a Partnership.
* Part IV   - Identification of Related Organizations Taxable as a Corporation or Trust
* Part V    - Transactions with Related Organizations
* Part VI   - Unrelated Organizations Taxable as a Partnership
* Part VII  - Supplemental Information
 

## Data Dictionary

```{r, echo=F, results='asis'}

dat <- read.csv( "../CONCORDANCE_V1.csv" )

d2 <- dat[ c("VARIABLE_NAME","SCOPE","DESCRIPTION","LOCATION_CODE") ]

d2 <- d2[  order( d2$VARIABLE_NAME, - rank(d2$LOCATION_CODE) )  , ]

d2 <- d2[ ! duplicated(d2$VARIABLE_NAME), ]

d2 <- d2[  order( d2$LOCATION_CODE )   , ]

row.names( d2 ) <- NULL


kable( d2 )

```




```{css}
p {
color: black;
margin: 0 0 20px 0;
}

td {
    padding: 3px 10px 3px 10px;
    text-align: center;
}

table
{ 
    margin-left: auto;
    margin-right: auto;
    margin-top:80px;
    margin-bottom:100px;
}

h1, h2{
  margin-top:100px;
  margin-bottom:20px;
}


h3{
  margin-top:100px;
  margin-bottom:20px;
  background: lightgray;
}



H5{
    text-align: center;
    color: gray;
    font-size:0.8em;
}

img {
    max-width: 90%;
    display: block;
    margin-right: auto;
    margin-left: auto;
    margin-top:30px;
    margin-bottom:20px;
}

pre {
  overflow-x: auto;
}

pre code {
   display: block; 
   padding: 0.5em;
   margin-bottom:20px;
}

code {
  font-size: 92%;
  border: 10px solid #F8F8F8;
  margin-bottom: 2px;
}

code[class] {
  background-color: #F8F8F8;
}

```
